Repeatability of Pre-Flashover Fire Patterns on Gypsum Wallboard

### 2015-04-07 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Fix equation formatting.

Ratio from heat flux from source fire data 
vyto second item ignite

$\dot{q}'' = (\dot{Q} \chi_r)/(4 \pi\ R^2) $ \\

$\dot{q}''$ = heat flux per unit area $(kW/m^2)$ \\
$\dot{Q}$ = heat release rate $(kW)$ \\
$ \chi_r$ = radiative fraction \\
$R$ = distance from the point source to the target $(m)$ \\

Source fire plume temp and shape factor from vertical cylinder

$\dot{q}'' = \epsilon \sigma F_12 T^4 $ \\

$\epsilon$ = emissivity  \\
$\sigma$ = Stefan-Boltzmann Constant $(5.670373(21)×10^(−8) W/m^2 K^4)$  \\

@@

$Z_c = 0.08 dot{Q}^(2/5)$ \\

$Z_i = 0.20 dot{Q}^(2/5)$ \\

$Z_c$ = continuous flame height $(m)$  \\

$Z_i$ = intermittent flame height $(m)$ \\

@@

\subsection{Correlation Descriptions}
Heskestad, developed an empirical method for calculating the mean visible flame height for fuels which do not have substantial in-depth combustion.  Appropriate fuels would “include liquid pool fires and other horizontal surface fires” add cites.  Given that the fuel configurations are square, a conversion of the fuel surface area to the effective diameter is required in order to use Heskestad’s flame height equation directly.  Setting the area of the fuel surface, 0.093~$m^2$, equal to π $D^2$/4 and then solving for $D$ yields an effective diameter of 0.344~m.
Calculating the flame heights with the average peak heat release rates measured from the three fuels yields 1.0 m (3.3 ft), 1.0 m (3.3 ft), and 0.73 m (2.4 ft) for natural gas, gasoline, and polyurethane foam respectively. Taking the uncertainty of the measurements used to determine the heat release rate (±11~\%) into account generates a range of values.   The range of calculated values are compared with the  mean flame height and range for flame heights  based on photographic analysis for each of the fuels in Table z.

\begin{center} 
$ H_f = 0.235\: \dot{Q}^{(2/5)} - 1.02 D $  \\
\end{center}
$ H_f$ = flame height (m)  \\
$ \dot{Q}$ = heat release rate (kW) \\
$ D$ = diameter of burner (m)  \\

@@

Compare Natural Gas at 0.61 m from instrumented wall and at 0.0 m from instrumented wall - problem bounds.

>>>>

Ratio from heat flux from source fire data
vyto second item ignite
\begin{equation} \label{eq:second_item}
\dot{q}'' = (\dot{Q} \chi_r)/(4 \pi\ R^2)
\end{equation}
where $\dot{q}''$ is the heat flux per unit area kW/m$^2$, $\dot{Q}$ is the heat release rate (kW), $\chi_r$ is the radiative fraction, and $R$ = distance from the point source to the target (m).

Source fire plume temp and shape factor from vertical cylinder
\begin{equation}\label{eq:source_fire}
\dot{q}'' = \epsilon \sigma F_{12} T^4  \\
\end{equation}
where $\epsilon$ is the emissivity, $\sigma$ is the Stefan\-Boltzmann Constant (5.67 $\times 10^{−8}$~W/m$^2$~K$^4$) and $F_{12}$ is the radiative shape factor.

@@

\begin{equation}\label{eq:z_c}
Z_c = 0.08 \dot{Q}^{\frac{2}{5}}
\end{equation}
where $Z_c$ is the continuous flame height~(m)
\begin{equation}\label{eq:z_i}
Z_i = 0.20 \dot{Q}^{\frac{2}{5}}
\end{equation}
where $Z_i$ is the intermittent flame height~(m)

@@

\subsection{Correlation Descriptions}
Heskestad, developed an empirical method for calculating the mean visible flame height for fuels which do not have substantial in-depth combustion.  Appropriate fuels would “include liquid pool fires and other horizontal surface fires” add cites.  Given that the fuel configurations are square, a conversion of the fuel surface area to the effective diameter is required in order to use Heskestad’s flame height equation directly.  Setting the area of the fuel surface, 0.093~m$^2$, equal to $\pi D^2/4$ and then solving for $D$ yields an effective diameter of 0.344~m.
Calculating the flame heights with the average peak heat release rates measured from the three fuels yields 1.0~m and 0.73~m for natural gas, gasoline, and polyurethane foam respectively. Taking the uncertainty of the measurements used to determine the heat release rate ($\pm$ 11~\%) into account generates a range of values.   The range of calculated values are compared with the  mean flame height and range for flame heights  based on photographic analysis for each of the fuels in Table z.

\begin{equation}\label{eq:flame_height}
H_f = 0.235\: \dot{Q}^{\frac{2}{5}} - 1.02 D
\end{equation}
where $H_{f}$ is the flame height (m), $\dot{Q}$ is the heat release rate (kW), and $D$ is the burner diameter (m).

@@

Compare Natural Gas at 0.61~m from instrumented wall and at 0.0~m from instrumented wall - problem bounds.
